Painting with Triangles

### 2014-04-22 paper.tex
figure rearrange
Made a few minor changes to sentences that had extra words etc.

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcsfinal}
    \caption{Color arcs. Orange lines are boundary edges, and together with black lines form the triangle
    mesh. Each point is given more or more color arcs, 
    which stores the color of triangle corners in that angular range.
    Points in the middle row have red arcs on top and blue below,
    yielding triangles with those colors, separated by a hard boundary.}
    \label{fig:arcs}
\end{figure}

@@

\begin{figure}[t]
    \centering
        \fbox{\includegraphics[width=0.45\textwidth]{images/gradientarcs}}
    \caption{A close look at a gradient stroke. The blue edges are boundaries where
    the points have gray color arcs as shown. The purple edges are boundaries where
    the points have transparent gray color arcs. This gives triangles connecting the two boundaries
    a linear gradient from gray to white.}
    \label{fig:softarcs}
\end{figure}

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:boxes}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision.

@@

Figure~\ref{fig:numtriangles} shows the zooming case grows linearly while the non-zooming case
appears to grow quadratically. This is expected since every new stroke has the chance to overlap
all of the old strokes. Therefore each new stroke does not just add a constant amount of geometry, but 
due to intersections with previous strokes extra intersection points are added. This results in a linear
increase in the amount of geometry per new stroke, yielding a quadratic growth rate overall. 
However, in the zooming case each stroke rarely overlaps previous strokes, and therefore
intersection points are rarely added. In this case the geometry increases by a constant amount per stroke, which yields a linear growth rate.

@@

\subsection{Performance}
The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to render. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take an arbitrarily long.
% This brings us to the final point, simplification.

@@

\section{Conclusion and Future Work}
Our system enables a user to paint like they would in a raster graphics program 
to create vector graphics. The core element is a triangle mesh representation of the painting.
We have created an algorithm to convert a user's mouse motions into a triangle mesh, and then composite that mesh on the preexisting mesh containing the previous strokes.

>>>>

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcsfinal}
    \caption{Color arcs. Orange lines are boundary edges, and together with black lines form the triangle
    mesh. Each point is given one or more color arcs 
    which store the color of triangle corners in that angular range.
    Points in the middle row have red arcs on top and blue below,
    yielding triangles with those colors, separated by a hard boundary.}
    \label{fig:arcs}
\end{figure}

@@

\begin{figure}[t]
    \centering
        \fbox{\includegraphics[width=0.45\textwidth]{images/gradientarcs}}
    \caption{A close look at a gradient stroke. The blue edges are boundaries where
    the points have gray color arcs as shown. The purple edges are boundaries where
    the points have white color arcs. This gives triangles connecting the two boundaries
    a linear gradient from gray to white.}
    \label{fig:softarcs}
\end{figure}

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision.

@@

Figure~\ref{fig:numtriangles} shows the zooming case grows linearly while the non-zooming case
appears to grow quadratically. This is expected since in the non-zooming case every new stroke has the chance to overlap
all of the old strokes. Therefore each new stroke does not just add a constant amount of geometry, but 
due to intersections with previous strokes extra intersection points are added. This results in a linear
increase in the amount of geometry per new stroke, yielding a quadratic growth rate overall. 
However, in the zooming case each stroke rarely overlaps previous strokes, and therefore
intersection points are rarely added. In this case the geometry increases by a constant amount per stroke, which yields a linear growth rate.

@@

\subsection{Performance}
The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to render. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take arbitrarily long.
% This brings us to the final point, simplification.

@@

\section{Conclusion and Future Work}
Our system enables a user to paint like they would in a raster graphics program 
to create vector graphics. The core element is a triangle mesh representation of the painting.
We have created an algorithm to convert a user's mouse motions into a triangle mesh, and then composite it onto the preexisting mesh containing the previous strokes.
